Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-26 inst/examples/20170201-manuscript.Rmd
trying to fix fig 3
Fig 8-9 update adding Other publication places

pics <- list()
for (catal in unique(df00$catalog)) {

@@

top <- c("Turku", "Vaasa", "Vyborg")
df <- df %>%	
        filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place, publisher)

@@

# Selected publication places
top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
df <- df %>%	
        filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place, publisher)

@@

```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
df <- df0
catal <- "Kungliga"
df <- df %>%
        filter(catalog == catal) %>%
	filter(country == "Finland" | publication_place == "Vyborg") %>%
        filter(publication_year >= 1640 & publication_year <= 1828)

@@

# Selected publication places
top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
df <- df %>%	
        filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place, publisher)

>>>>

pics <- list()
for (catal in unique(df.full$catalog)) {

@@

top <- c("Turku", "Vaasa", "Vyborg")
df <- filter(df, !is.na(publication_place))
df$publication_place[!df$publication_place %in% top] <- "Other/Fennica"
top <- c(top, "Other/Fennica")
df <- df %>%	
        #filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place, publisher)

@@

# Selected publication places
top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
df <- filter(df, !is.na(publication_place))
df$publication_place[!df$publication_place %in% top] <- "Other/Kungliga"
top <- c(top, "Other/Kungliga")
df <- df %>%	
        #filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place, publisher)

@@

```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
df <- df0
catal <- "Kungliga"
df <- df %>%
        filter(catalog == catal) %>%
	#filter(country == "Finland" | publication_place == "Vyborg") %>%
        filter(publication_year >= 1640 & publication_year <= 1828)

@@

# Selected publication places
top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
df <- filter(df, !is.na(publication_place))
df$publication_place[!df$publication_place %in% top] <- "Other/Kungliga"
top <- c(top, "Other/Kungliga")
df <- df %>%	
        filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place, publisher)
